\chapter{General discussion and conclusions}\label{Chap5}

Many studies focused on survival during the early life history stages, and the causal mechanisms and how impacts on subsequent recruitment. Of the various recruitment hypotheses, those regarding starvation can be addressed by the Ichthyop-DEB tool developed in this manuscript. For example, critical period hypothesis (Hjort 1914).\\

One of the first questions we can ask ourselves when choosing a model to try to answer a scientific question is: Why trust this model? And furthermore, how complex does this model need to be? This will depend on the question, the scale of the process to be studied and the precedents of the answers to this question.\\

for the most part of fisheries is how good is the recruitment of the species. This is already a complex process that includes different agents such as environmental conditions, the state of its adult population or its adaptive capacity.\\
 
In this context of study, the Peruvian anchovy has been well studied, from associating environmental variables to the presence of large schools at the time of fishing to having models with equations that describe how the environment impact the species at different levels as well as the frequency and detail of the monitoring system that is targeted each year. We have focused on the modeling approach.\\

Here we present the development of a modeling tool that aims to understand the impact of temperature and food availability on recruitment and survival of early life stages of aquatic species through an individual-based modeling approach (Fig. 5.1). This approach was born from adding complexity to a larval dispersal model (Brochier et al. 2008; Lett et al. 2008) to which a module was added to simulate growth using a DEB bioenergetic model (Kooijman 2009). The results of the present study give robustness to previous results (Brochier et al. 2008) on larval retention patterns where we agree that spawning depth plays a very important role in addition to a seasonal variation that depends on depth. This is quite interesting considering that over the years new versions of the hydrodynamic model of coastal circulation off Peru have been created, and these updates have maintained the general patterns. (replicabilidad de resultados, ). We can conclude that to work on E. ringens recruitment simulations, in order to save computational time and energy, we can continue with a spatial resolution of 10 km. In addition, it is recommended to use the coastal behavior called standstill, since for the purposes of our research it will not significantly affect near-shore particle transport.\\

In Peru, small pelagic fish monitoring is based on spawning biomass estimation and egg and larvae surveys (Pauly and Soriano 1987; Ayón 2000; Gutiérrez et al. 2012) without explicitly accounting for spatial features (e.g. cross-shore and vertical). However, our results shows that spatial and vertical distribution also largely impact the success of recruitment. We suggest this information should be included in coupled model and observation operational system, which allows to forecast the seasonal success of recruitment. Thus, spatial monitoring of ichthyoplankton distribution should include assessment of vertical distribution. This can be achieved using multinet or, for a faster processing of the information, in situ imaging system that may allow a rapid processing (Orenstein et al. 2020).\\